PANCHANGE_data_preprocessing

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
added the additional mhd columns to the finalised mhd tibble

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  select(all_of(disorder_columns)) %>%
  mutate(
    disorders_total_count =
      rowSums(.)
  )

@@

Comorbidity count
```{r}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    comorbidity_total_count = 
      case_when(
        disorders_total_count == 1 ~ 0,
        disorders_total_count > 1 ~ disorders_total_count - 1
  )
  )

glad.mhd.raw.id %>%
  freq(comorbidity_total_count,
       cumul = F)
```

@@

Create new dataframe with the derived categories
++KT: do we want to keep individual diagnoses here as well?? 
```{r glad mhd categories}
glad.mhd.raw.categories <- glad.mhd.raw.id %>%
  select(
    Sample,
    ID,
    anxiety_disorders_numeric,
    anxiety_disorders,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.social_anxiety_or_social_phobia,
    agoraphobia_panic_disorder_numeric,
    agoraphobia_panic_disorder,
    depressive_disorders_numeric,
    depressive_disorders,
    eating_disorders_numeric,
    eating_disorders,
    obsessive_compulsive_disorders_numeric,
    obsessive_compulsive_disorders,
    psychotic_disorders_numeric,
    psychotic_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.posttraumatic_stress_disorder_ptsd_numeric,
    mhd.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder_numeric,
    mhd.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_numeric,
    mhd.personality_disorder,
    personality_cluster_a_numeric,
    personality_cluster_a,
    personality_cluster_b_numeric,
    personality_cluster_b,
    personality_cluster_c_numeric,
    personality_cluster_c
    )
```

>>>>

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    disorders_total_count =
      rowSums(.[disorder_columns])
  )

@@

Comorbidity count
```{r cormorbidity_total_count}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    comorbidity_total_count_numeric = 
      case_when(
        disorders_total_count == 1 ~ 0,
        disorders_total_count > 1 ~ disorders_total_count - 1
  )
  )

glad.mhd.raw.id %>%
  freq(comorbidity_total_count_numeric,
       cumul = F)
```

```{r}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    comorbidity_total_count_factor_numeric =
      case_when(
    comorbidity_total_count_numeric == "0" ~ 0,
    comorbidity_total_count_numeric == "1" ~ 1,
    comorbidity_total_count_numeric == "2" ~ 2,
    comorbidity_total_count_numeric > 2 ~ 3
    )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    comorbidity_total_count_factor =
      recode_factor(comorbidity_total_count_factor_numeric,
                    "0" = "No comorbidity",
                    "1" = "1 comorbid disoder",
                    "2" = "2 comorbid disoders",
                    "3" = "3+ comorbid disoder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(comorbidity_total_count_factor,
       cumul = F)
```

@@

Create new dataframe with the derived categories
++KT: do we want to keep individual diagnoses here as well?? 
```{r glad mhd categories}
glad.mhd.raw.categories <- glad.mhd.raw.id %>%
  select(
    Sample,
    ID,
    anxiety_disorders_numeric,
    anxiety_disorders,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.social_anxiety_or_social_phobia,
    agoraphobia_panic_disorder_numeric,
    agoraphobia_panic_disorder,
    depressive_disorders_numeric,
    depressive_disorders,
    eating_disorders_numeric,
    eating_disorders,
    obsessive_compulsive_disorders_numeric,
    obsessive_compulsive_disorders,
    psychotic_disorders_numeric,
    psychotic_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.posttraumatic_stress_disorder_ptsd_numeric,
    mhd.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder_numeric,
    mhd.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_numeric,
    mhd.personality_disorder,
    personality_cluster_a_numeric,
    personality_cluster_a,
    personality_cluster_b_numeric,
    personality_cluster_b,
    personality_cluster_c_numeric,
    personality_cluster_c,
    depression_and_anxiety_numeric,
    depression_and_anxiety,
    restricting_vs_binge_eating_eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    bipolar_and_schizophrenia_numeric,
    bipolar_and_schizophrenia,
    control_numeric,
    control,
    disorders_total_count,
    comorbidity_total_count_numeric,
    comorbidity_total_count_factor_numeric,
    comorbidity_total_count_factor
    )
```
